Performance of two different ontological and data access methods

### 2014-07-03 cold2014/magnus.tex
wrapfigging
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@719 43ef1190-90fd-4dd7-a769-d0121f02b80e

\documentclass{llncs}
\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{cite}
\usepackage{verbatim}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{listings}

@@

\begin{figure}
  \centering
      \includegraphics[width=12cm]{initialView.png}
  \caption{Initial view for a user}\label{initialView}
\end{figure}

@@

%\begin{table}
%\begin{center}
%    \begin{tabular}{ | l | l  l  l |}
%    \hline
%    {\bf Run} &  {\bf Fuel type} & {\bf Transmission} & {\bf Speed} \\ \hline
%	 1 & Diesel & Automatic & 100 \\ \hline
%	 2 & Petrol & Automatic & 100 \\ \hline
%	 3 & Diesel & Manual & 100 \\ \hline
%	 4 & Petrol & Manual & 100 \\ \hline
%	 5 & Diesel & Automatic & 200 \\ \hline
%	 6 & Petrol & Automatic & 200 \\ \hline
%	 7 & Diesel & Manual & 200 \\ \hline
%	 8 & Petrol & Manual &  200 \\ \hline
%    \end{tabular}
%\end{center}
%\caption{A filled planning matrix with 3 factors}\label{designsspec}
%\end{table}

@@

\begin{table}[H]
\begin{center}
    \begin{tabular}{ | l | l l |}
    \hline
    {\bf Factor} & {\bf Level 1} & {\bf Level 2} \\ \hline
	Ontology & -vso & -co \\ \hline 
	Fuel type & Diesel & Unleaded Petrol \\ \hline 
	Transmission & Manual Gearbox & Automatic Gearbox \\ \hline 
    \end{tabular}
\end{center}
\caption{Factors and levels for experiment 1}\label{facandlevExp1}
\end{table}

The next step was to create the planning matrix for this
experiment. Table
\ref{3factor} shows all the 8 runs for the experiment with three
factors. We also ran a randomized version the experiment to check
whether the randomization would influence the experiment. The results
were almost equal which eliminated randomization as a factor.  Both
results can be found in appendix \ref{appD}. After each run the
response time were logged to that particular run. The response time
were then used to check for significant effect when the experiment
were evaluated
\begin{table}
\begin{center}
    \begin{tabular}{ | l | l l l |}
    \hline
    {\bf Run} & {\bf Ontology} & {\bf Fuel type} & {\bf Transmission} \\ \hline
	1 & -vso & Diesel & Automatic Gearbox \\ \hline 
	2 & -co & Diesel & Automatic Gearbox \\ \hline 
	3 & -vso & Unleaded Petrol & Automatic Gearbox \\ \hline 
	4 & -co & Unleaded Petrol & Automatic Gearbox \\ \hline 
	5 & -vso & Diesel & Manual Gearbox \\ \hline 
	6 & -co & Diesel & Manual Gearbox \\ \hline 
	7 & -vso & Unleaded Petrol & Manual Gearbox \\ \hline 
	8 & -co & Unleaded Petrol & Manual Gearbox \\ \hline 
    \end{tabular}
\end{center}
\caption{Planning matrix for experiment with three factors}\label{3factor}
\end{table}

Like the rest of the experiments we used DanielPlot to evaluate and a
package in R to visualize the result. The Figure \ref{3factorGraph}
shows the results.  Here we see no significant factors. Still there
are small effects from several factors. In Table \ref{3factorEffect}
we can see the time effects from largest to smallest.  We see that the
ontology factor has the largest effect on approximately 2.2 seconds
which means that one of the ontologies overall is 2.2 seconds
faster. By reading the results from the linear model it is the factor
level \textsf{-vso} which has an overall faster response time.

\begin{figure}
 \includegraphics[width=12cm]{2factorfinal.pdf}
  \caption{Resulting graph for the three factor experiment}\label{3factorGraph}
\end{figure}

\begin{table}
\begin{center}
    \begin{tabular}{ | l l |}
    \hline
    {\bf Factors} & {\bf Absolute Effect}  \\ \hline
	  O     & 2.2463476\\ \hline
	  O:T    &0.4536135 \\ \hline
	  O:FT:T &0.4534723 \\ \hline
	  T      &0.4513712 \\ \hline
	  FT:T   &0.4499820\\ \hline
	  O:FT   &0.1240831 \\ \hline
	  FT     &0.1189629 \\ \hline
    \end{tabular}
\end{center}
\caption{Table of effects for the three factor experiment}\label{3factorEffect}
\end{table}

@@

\begin{table}
\begin{center}
    \begin{tabular}{ | l l |}
    \hline
    {\bf Factors} & {\bf Absolute Effect}  \\ \hline
      O & 58.1785542324229 \\ \hline
      E:FC & 45.6971032050781 \\ \hline
      O:E:FC & 45.5502538925781\\ \hline
      FC & 38.6140886777344\\ \hline
      O:FC & 38.5571969433593\\ \hline
      O:E & 35.3967871113281\\ \hline
      E & 35.3827983613282\\ \hline
      O:T & 33.1249425527344\\ \hline
      T & 33.1154579746093\\ \hline
      O:T:E:FC & 29.3077075019531\\ \hline
      T:E:FC & 29.2986405957031\\ \hline
      O:T:FC & 28.2420862089844\\ \hline
      T:FC & 28.2325333808593\\ \hline
      O:T:E & 25.3121093378906\\ \hline
      T:E & 25.3039236347656\\ \hline
      WT:E & 11.9191989902344\\ \hline
      O:WT:E & 11.8908780371094\\ \hline
      O:WT:FC & 11.7234715332032\\ \hline
      WT:FC & 11.7140515488281\\ \hline
      O:D:E & 10.1241599902344\\ \hline
    \end{tabular}
\end{center}
\caption{The top twenty significant effects of the ten factor graph}\label{10factorEffect}
\end{table}

>>>>

\documentclass{llncs}
%\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{cite}
\usepackage{verbatim}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{listings}

@@

@@

%\begin{wraptable}
%\begin{center}
%    \begin{tabular}{ | l | l  l  l |}
%    \hline
%    {\bf Run} &  {\bf Fuel type} & {\bf Transmission} & {\bf Speed} \\ \hline
%	 1 & Diesel & Automatic & 100 \\ \hline
%	 2 & Petrol & Automatic & 100 \\ \hline
%	 3 & Diesel & Manual & 100 \\ \hline
%	 4 & Petrol & Manual & 100 \\ \hline
%	 5 & Diesel & Automatic & 200 \\ \hline
%	 6 & Petrol & Automatic & 200 \\ \hline
%	 7 & Diesel & Manual & 200 \\ \hline
%	 8 & Petrol & Manual &  200 \\ \hline
%    \end{tabular}
%\end{center}
%\caption{A filled planning matrix with 3 factors}\label{designsspec}
%\end{wraptable}

@@

\begin{wraptable}{l}{0.67\textwidth}
    \begin{tabular}{ | l | l l |}
    \hline
    {\bf Factor} & {\bf Level 1} & {\bf Level 2} \\ \hline
	Ontology & -vso & -co \\ \hline 
	Fuel type & Diesel & Unleaded Petrol \\ \hline 
	Transmission & Manual Gearbox & Automatic Gearbox \\ \hline 
    \end{tabular}
\caption{Factors and levels for experiment 1}\label{facandlevExp1}
\end{wraptable}

The next step was to create the planning matrix for this
experiment. Table
\ref{3factor} shows all the 8 runs for the experiment with three
factors. We also ran a randomized version the experiment to check
whether the randomization would influence the experiment. The results
were almost equal which eliminated randomization as a factor.  Both
results can be found in appendix \ref{appD}. After each run the
response time were logged to that particular run. The response time
were then used to check for significant effect when the experiment
were evaluated
\begin{wraptable}{l}{0.67\textwidth}
    \begin{tabular}{ | l | l l l |}
    \hline
    {\bf Run} & {\bf Ontology} & {\bf Fuel type} & {\bf Transmission} \\ \hline
	1 & -vso & Diesel & Automatic Gearbox \\ \hline 
	2 & -co & Diesel & Automatic Gearbox \\ \hline 
	3 & -vso & Unleaded Petrol & Automatic Gearbox \\ \hline 
	4 & -co & Unleaded Petrol & Automatic Gearbox \\ \hline 
	5 & -vso & Diesel & Manual Gearbox \\ \hline 
	6 & -co & Diesel & Manual Gearbox \\ \hline 
	7 & -vso & Unleaded Petrol & Manual Gearbox \\ \hline 
	8 & -co & Unleaded Petrol & Manual Gearbox \\ \hline 
    \end{tabular}
\caption{Planning matrix for experiment with three factors}\label{3factor}
\end{wraptable}

Like the rest of the experiments we used DanielPlot to evaluate and a
package in R to visualize the result. Figure \ref{3factorGraph}
shows only one significant factor, namely the \textsf{O} factor in the
upper right corner. In Table \ref{3factorEffect}
we can see the time effects from largest to smallest.  We see that the
ontology factor has the largest effect on approximately 2.2 seconds
which means that one of the ontologies overall is 2.2 seconds
faster. By reading the results from the linear model it is the factor
level \textsf{-vso} which has an overall faster response time.

\begin{wraptable}{l}{0.35\textwidth}
\vspace{-25pt}
    \begin{tabular}{ | l l |}
    \hline
    {\bf Factors} & {\bf Absolute Effect}  \\ \hline
	  O     & 2.2463476\\ \hline
	  O:T    &0.4536135 \\ \hline
	  O:FT:T &0.4534723 \\ \hline
	  T      &0.4513712 \\ \hline
	  FT:T   &0.4499820\\ \hline
	  O:FT   &0.1240831 \\ \hline
	  FT     &0.1189629 \\ \hline
    \end{tabular}
\caption{Table of effects for the three factor experiment}\label{3factorEffect}
\vspace{-65pt}
\end{wraptable}

\begin{figure}
 \includegraphics[width=12cm, height=8cm]{2factorfinal.pdf}
  \caption{Resulting graph for the three factor experiment}\label{3factorGraph}
\end{figure}

@@

\begin{wraptable}{l}{0.4\textwidth}
\vspace{-25pt}
    \begin{tabular}{ | l l |}
    \hline
    {\bf Factors} & {\bf Absolute Effect}  \\ \hline
      O & 58.1785542324229 \\ \hline
      E:FC & 45.6971032050781 \\ \hline
      O:E:FC & 45.5502538925781\\ \hline
      FC & 38.6140886777344\\ \hline
      O:FC & 38.5571969433593\\ \hline
      O:E & 35.3967871113281\\ \hline
      E & 35.3827983613282\\ \hline
      O:T & 33.1249425527344\\ \hline
      T & 33.1154579746093\\ \hline
      O:T:E:FC & 29.3077075019531\\ \hline
      T:E:FC & 29.2986405957031\\ \hline
      O:T:FC & 28.2420862089844\\ \hline
      T:FC & 28.2325333808593\\ \hline
      O:T:E & 25.3121093378906\\ \hline
      T:E & 25.3039236347656\\ \hline
      WT:E & 11.9191989902344\\ \hline
      O:WT:E & 11.8908780371094\\ \hline
      O:WT:FC & 11.7234715332032\\ \hline
      WT:FC & 11.7140515488281\\ \hline
      O:D:E & 10.1241599902344\\ \hline
    \end{tabular}
\caption{The top twenty significant effects of the ten factor graph}\label{10factorEffect}
      \vspace{-25pt}
\end{wraptable}
